Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-03-27 paper.tex
Fixes following meeting with @soudabeh19

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
% 2. columns
% 3. rows
% 4. random real
% 5. random diagonal
% 6. random triangular
% For every method, show a training matrix to illustrate for a given ratio.

>>>>

We investigated the following sampling techniques for the training set.

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
\paragraph{Random unreal}
The training set is sampled randomly with no restriction, that is,
regardless of their generation time.  This method will be used as a
baseline for comparison with other methods, although it is not
realistic.

% 2. columns
\paragraph{Complete columns}
The training set is sampled by randomly selecting complete columns in
the matrix, that is, complete subject executions. The last selected
column might be incomplete to meet the exact training ratio. This
method is realistic: it corresponds to a situation where the
collaborative filtering method will predict the reproducibility in the
remaining subjects from the subjects in the training set.

% 3. rows
\paragraph{Complete rows} The training set is sampled by randomly
selecting complete rows in the matrix, that is, the first files in
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a
situation where the processing of all the subjects is launched and
interrupted before the execution is complete. The collaborative
filtering method will then predict the reproducibility of the
remaining files.

% 4. random real
\paragraph{Random real}
\todo{Explain this better} This approach will select its next training set element according to
the next file turn in the next random selected subject.

% 5. random diagonal
\paragraph{Random diagonal}
For every subject, the number of files added to the training set is randomly picked from a uniform distribution.

% 6. random triangular
\paragraph{Random triangular}
To acquire about those files which are generated almost at the end of pipeline processing with respect of the training ratio, we used triangular ratio to calculate the number of files for each subject and added them to the training set.
% For every method, show a training matrix to illustrate for a given ratio.

\todo{Find better names: consistent with either the graphical patter or the distribution.}
\todo{Add a summary figure of the sampling methods.}
